Dynein project log

### 2016-09-05 thesis_stuff/thesis_stuff.tex
Add notes on Dynein pre-powerstroke crystal structure paper.

\section{Citations}
Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\

Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S. ``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural & Molecular Biology}. 2012, 19:193-200.\\

>>>>

\section{Citations}
\subsection{Annual Review, 8-state Mechanochemical diagram}
Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\

Goes over in detail the various steps of the Dynein chemical cycle. Links to a lot of good papers.\\

\subsection{Weihong's Dynein stepping data}
Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S. ``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural & Molecular Biology}. 2012, 19:193-200.\\

Has the stepping histograms we are trying to reproduce computationally.

\subsection{Pre-powerstroke structure, linker remodel details}
Schmidt, H*., Zalyte, R*., Urnavicius, L., Carter, AP. ``Structure of human cytoplasmic dynein-2 primed for its power stroke.'' \textit{Nature} 2014. 518:435-438.

Describes how ATP hydrolysis ``closes the ring,'' sterically interacting with the linker to cause the pre-powerstroke conformation. Does so by presenting the crystal structure of Dynein AAA1-ADP.Vanadate. Goes over AAs responsible for nucleotide binding. Supplemental video of AAA1L-AAA2L gap closing in response to nucleotide-Vi binding. Supplemental video of linker swinging in response to ring closure. AAA2-4 system acts rigidly during the cycle. Discusses how steric clash is what makes the linker take on a 90-degree bent shape when the ring closes. Figure on Dynein-ADP buttress having no kink, whereas Dynein-ADP.Vi having a kink. The kink presumably changes MTDB binding affinity.
